### 2024-03-23 doc/sections/mav-syntax.tex
Proposed unit-cautious version of `switch
Push changes before rewrite
Stuff

TODO: introduce MAV and Deep Inference.

Formulas:
\begin{displaymath}
  P, Q
  \Coloneq A^{+}
  \mid     A^{-}
  \mid     \Unit
  \mid     P \Tens Q
  \mid     P \Parr Q
  \mid     P \With Q
  \mid     P \Plus Q
  \mid     P \Seq  Q
\end{displaymath}

Negation:
\begin{displaymath}
  \begin{array}{lcl}
    \Dual(\Pos(A))   & = & \Neg(A)                 \\
    \Dual(\Neg(A))   & = & \Pos(A)                 \\
    \Dual(\Unit)     & = & \Unit                   \\
    \Dual(P \Tens Q) & = & \Dual(P) \Parr \Dual(Q) \\
    \Dual(P \Parr Q) & = & \Dual(P) \Tens \Dual(Q) \\
    \Dual(P \With Q) & = & \Dual(P) \Plus \Dual(Q) \\
    \Dual(P \Plus Q) & = & \Dual(P) \With \Dual(Q) \\
    \Dual(P \Seq  Q) & = & \Dual(P) \Seq  \Dual(Q)
  \end{array}
\end{displaymath}

>>>>

\begin{itemize}
  \item Structural equivalences are explicit.
  \item Inference is a congruence.
  \item Inference rules are unary.
  \item Relate to usual presentation of MALL.
  \item Relate to usual presentation of BV.
\end{itemize}

Formulas:
\begin{displaymath}
  \vP,\vQ
  \Coloneq \vPos\vA
  \mid     \vNeg\vA
  \mid     \vUnit
  \mid     \vP\vSeq \vQ
  \mid     \vP\vTens\vQ
  \mid     \vP\vParr\vQ
  \mid     \vP\vWith\vQ
  \mid     \vP\vPlus\vQ
\end{displaymath}

Negation:
\begin{displaymath}
  \begin{array}{
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l}
    \vDual{\vPos\vA}     & \vNeg\vA
                         &
    \vDual{\vUnit}       & \vUnit
                         &
    \vDual{\vP\vTens\vQ} & \vDual\vP \vParr \vDual\vQ
                         &
    \vDual{\vP\vParr\vQ} & \vDual\vP \vTens \vDual\vQ
    \\
    \vDual{\vNeg\vA}     & \vPos\vA
                         &
    \vDual{\vP\vSeq \vQ} & \vDual\vP \vSeq  \vDual\vQ
                         &
    \vDual{\vP\vWith\vQ} & \vDual\vP \vPlus \vDual\vQ
                         &
    \vDual{\vP\vPlus\vQ} & \vDual\vP \vWith \vDual\vQ
  \end{array}
\end{displaymath}

Inference rules:
\begin{displaymath}
  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vP\vParr\vDual\vP
     & \vUnit
     & \RuleLabel{axiom}
    \\
    \vUnit
     & \vP\vTens\vDual\vP
     & \RuleLabel{cut}
    \\
    \vUnit\vWith\vUnit
     & \vUnit
     & \RuleLabel{tidy}
    \\
    (\vP\vTens\vQ)\vParr\vR
     & \vP\vTens(\vQ\vParr\vR)
     & \RuleLabel{switch}
    \\
    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
     & \RuleLabel{sequence}
    \\
    \vP\vPlus\vQ
     & \vP
     & \RuleLabel{left}
    \\
    \vP\vPlus\vQ
     & \vQ
     & \RuleLabel{right}
    \\
    (\vP\vWith\vQ)\vParr\vR
     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
     & \RuleLabel{external}
    \\
    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
     & \RuleLabel{medial}
  \end{array}
\end{displaymath}

Equivalence rules:
\begin{displaymath}
  \begin{array}{
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll}
    \vP\vSeq\vUnit
     & \vP
     & \RuleLabel*[seq-runit]{\vSeq-Unit\textsuperscript{R}}
     &
    \vUnit\vSeq\vP
     & \vP
     & \RuleLabel*[seq-lunit]{\vSeq-Unit\textsuperscript{L}}
     &
    \vP\vSeq(\vQ\vSeq\vR)
     & (\vP\vSeq\vQ)\vSeq\vP
     & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
    \\
    \vP\vTens\vUnit
     & \vP
     & \RuleLabel*[tens-unit]{\vTens-Unit}
     &
    \vP\vTens\vQ
     & \vQ\vTens\vP
     & \RuleLabel*[tens-comm]{\vTens-Comm}
     &
    \vP\vTens(\vQ\vTens\vR)
     & (\vP\vTens\vQ)\vTens\vP
     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
    \\
    \vP\vParr\vUnit
     & \vP
     & \RuleLabel*[parr-unit]{\vParr-Unit}
     &
    \vP\vParr\vQ
     & \vQ\vParr\vP
     & \RuleLabel*[parr-comm]{\vParr-Comm}
     &
    \vP\vParr(\vQ\vParr\vR)
     & (\vP\vParr\vQ)\vParr\vP
     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
  \end{array}
\end{displaymath}

We write $\vEquiv$ for invertible inference rules, \ie $\vP\vEquiv\vQ$ means $\vP\vInfer\vQ$ and $\vQ\vInfer\vP$.

We write $\vInfer*$ for the reflexive, transitive closure of $\vInfer$.
